---
title: "team"
author: "Danny Nguyen & COnnor Hergenreter" 
date: "February 11, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. What is the overall number of chocolate bars rated?
Based on the summary statistics, the average/mean rating is approximately 3.191.
```{r}
summary(choco)
mean(choco$Rating)
```
2. How does the number of ratings depend on the year? Draw a bar chart of the number of reports.
Based on the bar chart. The number of ratings appears to have gradually increased with a slight decline in the last few years.
```{r}
barplot(table(choco$Review.Date), main="Number of Reports per Year", xlab="Review Year", ylab="Number of Reports")
```
3. How do ratings compare across different company locations? Focus on the three locations with the most ratings. (Hint: They are U.S.A., France, and Canada, but find them out using codes.)


4. Brainstorm and write down an interesting question that can be answer from the dataset. The question should not duplicate the questions above.


5. Answer the question from the dataset.

https://github.com/dannyn95/ds202_lab2

